---
title: "SugenFvsM"
output:
  pdf_document: default
  word_document: default
  html_document: default
date: "2024-02-13"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/skacar/OneDrive - Indiana University/PULMONARY POST DOC/Single_cell_Dr_Rafikov/PROJECT_SUGEN_SEX_DIFFERENCE")
```

# A- LOAD REQUIRED LIBRARY

```{r}

library(Seurat)
library(ggplot2)
library(cowplot)
library(gridExtra)

```

## 1- Load Functions

```{r}
 source("C:/Users/skacar/OneDrive - Indiana University/PULMONARY POST DOC/Single_cell_Dr_Rafikov/Sedat_Functions/Functions_SKR.R")

```

## 2- List All H5 Filtered_Feature_Bc_Matrix

```{r, eval=FALSE}
Sugen_Filtered <- list.files(path = "/Sugen_Ec_Filtered", pattern = "//.h5$", full.names = TRUE)
```

# B- LOAD THE FILTERED_BC_MATRIXES

```{r, eval=FALSE}

paste(getwd())

WTECF1_21_1 <- Read10X_h5(paste(getwd(), "Sugen_Ec_Filtered", "WTECF1_21_filtered_feature_bc_matrix.h5", sep = "/"))
WTECF2_21_2 <- Read10X_h5(paste(getwd(), "Sugen_Ec_Filtered", "WTECF2_21_filtered_feature_bc_matrix.h5", sep = "/"))
SUECF1_22_3 <- Read10X_h5(paste(getwd(), "Sugen_Ec_Filtered", "SUECF1_22_filtered_feature_bc_matrix.h5", sep = "/"))
SUECF2_22_4 <- Read10X_h5(paste(getwd(), "Sugen_Ec_Filtered", "SUECF2_22_filtered_feature_bc_matrix.h5", sep = "/"))
WTECM1_27_5 <- Read10X_h5(paste(getwd(), "Sugen_Ec_Filtered", "WTECM1_27_filtered_feature_bc_matrix.h5", sep = "/"))
WTECM2_27_6 <- Read10X_h5(paste(getwd(), "Sugen_Ec_Filtered", "WTECM2_27_filtered_feature_bc_matrix.h5", sep = "/"))
SUECM1_28_7 <- Read10X_h5(paste(getwd(), "Sugen_Ec_Filtered", "SUECM1_28_filtered_feature_bc_matrix.h5", sep = "/"))
SUECM2_28_8 <- Read10X_h5(paste(getwd(), "Sugen_Ec_Filtered", "SUECM2_28_filtered_feature_bc_matrix.h5", sep = "/"))
```

## 1- Make a Seurat Object for Each

```{r, eval=FALSE}
WTECF1_21_1 <- CreateSeuratObject(WTECF1_21_1, min.cells=3, min.features = 200)
WTECF2_21_2 <- CreateSeuratObject(WTECF2_21_2, min.cells=3, min.features = 200)
SUECF1_22_3 <- CreateSeuratObject(SUECF1_22_3, min.cells=3, min.features = 200)
SUECF2_22_4 <- CreateSeuratObject(SUECF2_22_4, min.cells=3, min.features = 200)
WTECM1_27_5 <- CreateSeuratObject(WTECM1_27_5, min.cells=3, min.features = 200)
WTECM2_27_6 <- CreateSeuratObject(WTECM2_27_6, min.cells=3, min.features = 200)
SUECM1_28_7 <- CreateSeuratObject(SUECM1_28_7, min.cells=3, min.features = 200)
SUECM2_28_8 <- CreateSeuratObject(SUECM2_28_8, min.cells=3, min.features = 200)
```

## 2- Make *A Sugrat_List* from all seurat objects

```{r, eval=FALSE}

sugrat_list <- list(
  WTECF1_21_1 = WTECF1_21_1,
  WTECF2_21_2 = WTECF2_21_2,
  SUECF1_22_3 = SUECF1_22_3,
  SUECF2_22_4 = SUECF2_22_4,
  WTECM1_27_5 = WTECM1_27_5,
  WTECM2_27_6 = WTECM2_27_6,
  SUECM1_28_7 = SUECM1_28_7,
  SUECM2_28_8 = SUECM2_28_8
)

```

## 3- Save the Sugrat_List

```{r, eval=FALSE}

saveRDS(sugrat_list, "sugrat_list.Rds")


```

 
## 4- Load the Sugrat_List

```{r}

sugrat_list <- readRDS("sugrat_list.Rds")


```

## 5- S_obj/Sugrat_List Separation

```{r}

  WTECF1_21_1 <- sugrat_list[["WTECF1_21_1"]]
  WTECF2_21_2 <- sugrat_list[["WTECF2_21_2"]]
  SUECF1_22_3 <- sugrat_list[["SUECF1_22_3"]]
  SUECF2_22_4 <- sugrat_list[["SUECF2_22_4"]]
  WTECM1_27_5 <- sugrat_list[["WTECM1_27_5"]]
  WTECM2_27_6 <- sugrat_list[["WTECM2_27_6"]]
  SUECM1_28_7 <- sugrat_list[["SUECM1_28_7"]]
  SUECM2_28_8 <- sugrat_list[["SUECM2_28_8"]]

rm(sugrat_list)

```

# C- MAKING A Seurat_List

```{r}

seurat_list <- list(
  A_WT_F = A_WT_F,
  B_SU_F = B_SU_F,
  C_WT_M = C_WT_M,
  D_SU_M = D_SU_M,
  A_WT_F_2 = A_WT_F_2,
  B_SU_F_2 = B_SU_F_2,
  C_WT_M_2 = C_WT_M_2,
  D_SU_M_2 = D_SU_M_2
)

```

## 1- First_batch: Assigning Sugrat_List to Seurat_List

```{r}

A_WT_F <- WTECF1_21_1
B_SU_F <- SUECF1_22_3
C_WT_M <- WTECM1_27_5
D_SU_M <- SUECM1_28_7

rm(WTECF1_21_1, SUECF1_22_3, WTECM1_27_5, SUECM1_28_7)

```

## 2- Second_batch: Assigning Sugrat_List to Seurat_List

```{r}

A_WT_F_2 <- WTECF2_21_2
B_SU_F_2 <- SUECF2_22_4
C_WT_M_2 <- WTECM2_27_6
D_SU_M_2 <- SUECM2_28_8

rm(WTECF2_21_2, SUECF2_22_4, WTECM2_27_6, SUECM2_28_8)
```

## 3- S_obj/Seurat_List Separation

```{r}

  A_WT_F <- seurat_list[["A_WT_F"]]
  B_SU_F <- seurat_list[["B_SU_F"]]
  C_WT_M <- seurat_list[["C_WT_M"]]
  D_SU_M <- seurat_list[["D_SU_M"]]
  A_WT_F_2 <- seurat_list[["A_WT_F_2"]]
  B_SU_F_2 <- seurat_list[["B_SU_F_2"]]
  C_WT_M_2 <- seurat_list[["C_WT_M_2"]]
  D_SU_M_2 <- seurat_list[["D_SU_M_2"]]
  
```

## 4- Make Sugen_List 1 $ 2

```{r, eval=FALSE}

sugen_list1 <- list(
  A_WT_F = A_WT_F,
  B_SU_F = B_SU_F,
  C_WT_M = C_WT_M,
  D_SU_M = D_SU_M
  )


sugen_list2 <- list(
  A_WT_F_2 = A_WT_F_2,
  B_SU_F_2 = B_SU_F_2,
  C_WT_M_2 = C_WT_M_2,
  D_SU_M_2 = D_SU_M_2
)
```
## 5- S_obj/ Sugen_List 1 & 2 Separation

```{r, eval=FALSE}

  A_WT_F <- sugen_list1[["A_WT_F"]]
  B_SU_F <- sugen_list1[["B_SU_F"]]
  C_WT_M <- sugen_list1[["C_WT_M"]]
  D_SU_M <- sugen_list1[["D_SU_M"]]
  A_WT_F_2 <- sugen_list2[["A_WT_F_2"]]
  B_SU_F_2 <- sugen_list2[["B_SU_F_2"]]
  C_WT_M_2 <- sugen_list2[["C_WT_M_2"]]
  D_SU_M_2 <- sugen_list2[["D_SU_M_2"]]
  
```


# D- MITOCHONDRIAL CLEANING STARTING...

## 1- Check the existence of MT genes 

```{r}
# Check if RNA_Seq assay is available

 mt_genes <- rownames(A_WT_F)[grep("Mt-", rownames(A_WT_F))]

print(mt_genes)

```

## 2- Generate "MT percentage" Column with perncet_mt function

```{r}

sugrat_list <- lapply(sugrat_list, percent_mt)

#percent_mt is a function!
```

## 3- MT Plots

### a- nCount_RNA Violin Plot

```{r, fig.height=5, fig.width=10}

library(gridExtra)

p1 <- VlnPlot(A_WT_F, features = "nCount_RNA") + geom_hline(yintercept = c(2000, 25000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none" ) + ggtitle("WT_Female")
p2 <- VlnPlot(B_SU_F, features = "nCount_RNA") + geom_hline(yintercept = c(2000, 25000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Female") 

p3 <- VlnPlot(C_WT_M, features = "nCount_RNA") + geom_hline(yintercept = c(2000, 25000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Male") 

p4 <- VlnPlot(D_SU_M, features = "nCount_RNA") + geom_hline(yintercept = c(2000, 25000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Male")  


#grid.arrange(p1, p2, p3, p4, ncol = 2)
#p <- p1 + p2 + p3 + p4
plot_row <- plot_grid(p1, p2, p3, p4, ncol = 4, align = "h")


print(plot_row)
```

### b- nFeature_RNA Violin Plot

```{r, fig.height=5, fig.width=10}

library(gridExtra)

p1 <- VlnPlot(A_WT_F, features = "nFeature_RNA") + geom_hline(yintercept = c(6000, 200), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Female")
p2 <- VlnPlot(B_SU_F, features = "nFeature_RNA") + geom_hline(yintercept = c(6000, 200), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Female") 

p3 <- VlnPlot(C_WT_M, features = "nFeature_RNA") + geom_hline(yintercept = c(6000, 200), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Male") 

p4 <- VlnPlot(D_SU_M, features = "nFeature_RNA") + geom_hline(yintercept = c(6000, 200), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Male")  


#grid.arrange(p1, p2, p3, p4, ncol = 2)
#p <- p1 + p2 + p3 + p4
plot_row <- plot_grid(p1, p2, p3, p4, ncol = 4, align = "h")


print(plot_row)
```

### c- percent.mt Violin Plot


```{r, fig.height=5, fig.width=10}

library(gridExtra)

p1 <- VlnPlot(A_WT_F, features = "percent.mt") + geom_hline(yintercept = 15, linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Female")
p2 <- VlnPlot(B_SU_F, features = "percent.mt") + geom_hline(yintercept = 15, linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Female") 

p3 <- VlnPlot(C_WT_M, features = "percent.mt") + geom_hline(yintercept = 15, linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Male") 

p4 <- VlnPlot(D_SU_M, features = "percent.mt") + geom_hline(yintercept = 15, linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Male")  


#grid.arrange(p1, p2, p3, p4, ncol = 2)
#p <- p1 + p2 + p3 + p4
plot_row <- plot_grid(p1, p2, p3, p4, ncol = 4, align = "h")


print(plot_row)
```

### d- nFeature vs nCount

```{r, fig.height=5, fig.width=15}

library(gridExtra)

p1 <- FeatureScatter(A_WT_F, feature1 = "nCount_RNA", feature2 = "nFeature_RNA") + geom_hline(yintercept = 6000, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = c(2000, 30000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Female")

p2 <- FeatureScatter(B_SU_F,  feature1 = "nCount_RNA", feature2 = "nFeature_RNA") + geom_hline(yintercept = 6000, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = c(2000, 30000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Female") 

p3 <- FeatureScatter(C_WT_M,  feature1 = "nCount_RNA", feature2 = "nFeature_RNA") + geom_hline(yintercept = 6000, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = c(2000, 30000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Male") 

p4 <- FeatureScatter(D_SU_M,  feature1 = "nCount_RNA", feature2 = "nFeature_RNA") + geom_hline(yintercept = 6000, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = c(2000, 30000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Male")  


#grid.arrange(p1, p2, p3, p4, ncol = 2)
#p <- p1 + p2 + p3 + p4
plot_row <- plot_grid(p1, p2, p3, p4, ncol = 4, align = "h")


print(plot_row)
```

### e- nCount vs MT_percentage

```{r, fig.height=5, fig.width=15}

library(gridExtra)

p1 <- FeatureScatter(A_WT_F, feature1 = "nCount_RNA", feature2 = "percent.mt") + geom_hline(yintercept = 30, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = c(2000, 30000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Female")

p2 <- FeatureScatter(B_SU_F,  feature1 = "nCount_RNA", feature2 = "percent.mt") + geom_hline(yintercept = 30, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = c(2000, 30000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Female") 

p3 <- FeatureScatter(C_WT_M,  feature1 = "nCount_RNA", feature2 = "percent.mt") + geom_hline(yintercept = 30, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = c(2000, 30000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Male") 

p4 <- FeatureScatter(D_SU_M,  feature1 = "nCount_RNA", feature2 = "percent.mt") + geom_hline(yintercept = 30, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = c(2000, 30000), linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Male")  


#grid.arrange(p1, p2, p3, p4, ncol = 2)
#p <- p1 + p2 + p3 + p4
plot_row <- plot_grid(p1, p2, p3, p4, ncol = 4, align = "h")


print(plot_row)
```

### f - nFeatures vs MT_percentage

```{r, fig.height=5, fig.width=15}

library(gridExtra)

p1 <- FeatureScatter(A_WT_F, feature1 = "nFeature_RNA", feature2 = "percent.mt") + geom_hline(yintercept = 30, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = 6000, linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Female")

p2 <- FeatureScatter(B_SU_F,  feature1 = "nFeature_RNA", feature2 = "percent.mt") + geom_hline(yintercept = 30, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = 6000, linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Female") 

p3 <- FeatureScatter(C_WT_M,  feature1 = "nFeature_RNA", feature2 = "percent.mt") + geom_hline(yintercept = 30, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = 6000, linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("WT_Male") 

p4 <- FeatureScatter(D_SU_M,  feature1 = "nFeature_RNA", feature2 = "percent.mt") + geom_hline(yintercept = 30, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = 6000, linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle("SU_Male")  


#grid.arrange(p1, p2, p3, p4, ncol = 2)
#p <- p1 + p2 + p3 + p4
plot_row <- plot_grid(p1, p2, p3, p4, ncol = 4, align = "h")


print(plot_row)
```


## 4- Filtering




